Final Project

### 2025-05-05 MSSC5750_Project.qmd
Final Updates and Cleanup

summary(data$person_income)

@@

### cred hist length
ggplot(data=data %>% summarize(count=n(),.by=cb_person_cred_hist_length), aes(x= cb_person_cred_hist_length, y=count)) + geom_col(fill='steelblue') + ggtitle('Frequencies for credit history length')

@@

```{r}

@@

Adding LDA results to table
```{R}

@@

addresults2('LDA', confusionMatrix(factor( ifelse(temp$previous_loan_defaults_on_file=='Yes',0,temp$classify.loan_data.loan_status ) ), factor(temp$loan_data.loan_status), positive = '1'))
rownames(results2)<-NULL
```

>>>>

### quick summarizations to give us an idea of what we need to visualize/look closer at
summary(data$person_income)

@@

### cred hist length
ggplot(data=data %>% summarize(count=n(),.by=cb_person_cred_hist_length), aes(x= cb_person_cred_hist_length, y=count)) + geom_col(fill='steelblue') + ggtitle('Frequencies for credit history length') + scale_x_continuous(breaks=c(2,seq(10,30,5)) )

@@

```{r}
# Originally was using prior loan default as outcome variable
# Switched to loan_status to match the target variable we used for everything else

@@

Adding David's LDA results to table
```{R}

@@

addresults2('LDA', confusionMatrix(factor( ifelse(temp$previous_loan_defaults_on_file=='Yes',0,temp$classify.loan_data.loan_status ) ), factor(temp$loan_data.loan_status), positive = '1'))
rownames(results2)<-NULL

cbind("Model"=results[,1],round(results[,2:4],3))
cbind("Model"=results2[,1],round(results2[,2:4],3))
```
